Descriptions of four new species of \textit{Minyomerus} Horn, 1876 (Coleoptera: Curculionid\ae), with notes on their distribution and phylogeny

### 2018-03-01 tex/manuscript.tex
subsubsection, not subsection
Added a brief intro and edited methods

\section*{Introduction}
	\#
\section*{Materials and methods}
	\paragraph{Natural history observations} 
		Members of the genus Minyomerus are typically found on a variety of host plants, as indicated following each species account.
		Many species are likely generalists with regards to their host plant spectrum. 
		Adult weevils are most commonly observed on the leaves and branches of the host where they feed on the leaf tissue. Eggs, larvae, and pupae remain unknown. 
		The larvae are probably root feeders, as observed in the tanymecine genus Tanymecus Germar, 1817 (Howden 1975). 
		They typically inhabit arid regions, especially deserts, throughout southwestern North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
		They also occur in semi-arid regions of the Great Plains, on the Colorado Plateau, and throughout Baja California, Mexico. 
		The adults apparently disperse without flight, as the hind wings and associated flight structures of all species in the genus are greatly reduced and not readily apparent after dissections.
		In several species only females are known, and some are putatively considered parthenogenetic, as indicated in the respective descriptions.

	\paragraph{Acquisition of museum specimens} 
		Georeferencing of localities was performed with Google Earth (Google Inc. 2009–2015) and reported in decimal degrees.
		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2015).
		The set of existing \textit{Minyomerus} [JF2015] specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al. (1993):

@@

	\paragraph{Morphological analysis}
		The herein utilized systematic and descriptive approach follows Franz (2010a, 2010b, 2012).
		Terminology for exterior morphology is in general accordance with Torre-Bueno (Nichols 1989).
		Additional morphological terms specific to (entimine) weevils were used as follows:
			Ting (1936) and Morimoto and Kojima (2003) for mouthparts;
			Thompson (1992) for tibial apices and abdominal segments;
			and Oberprieler et al. (2014) and Howden (1995) for male and female terminalia.
		All measurements were taken using a Leica M205 C stereomicroscope and attached computer running the software Leica Application Suite (LAS), version 4.1.0.
		The overall body length and width were measured in dorsal view as the maximum distance between the apex of the rostrum and the apex of the elytra, and the maximum width of the elytra, respectively.
		The length of the rostrum was measured in dorsal view as the distance extending from the apex of the epistoma to the anterior margin of the eyes.
		The width of the rostrum was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		The length of the pronotum was measured in dorsal view as the length along the midline from the anterior margin to the posterior margin.
		The width of the elytra was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were performed in dorsal orientation, as the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, whereas habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.

		Species of Minyomerus [JF2015] recognized in this revision were delimited through application of the phylogenetic species concept sensu Wheeler and Platnick (2000).
		Species descriptions follow the inferred phylogenetic sequence (see details below).
		The genus-level description for Minyomerus [JF2015] highlights characters present in all members and accounts for their apparent variability.
		Consequently, the species descriptions represent unique and complementary accounts of the character states observed in each species, including their variability, and excepting characters that are invariate within the genus as specified in the higher-level description of Minyomerus.
		Likewise, descriptions of males in the genus- and species-level accounts emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		Some redundancy occurs between genus and species descriptions when discussing characters that vary widely within single species, and also between species descriptions where a character exhibits considerable variation in some species yet is invariant in others.
		The key to identifying species of Minyomerus is arranged with emphasis being placed on the most readily observable diagnostic characters.
		The revision is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

@@

		The morphological cladistic analysis includes 22 terminal taxa; with 17 ingroup and 5 outgroup terminals.

@@

		We used the modeling program Maxent, Version 3.3, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al. 2004, 2006; Elith et al. 2011).

@@

		However, no models could be created for three species with single documented localities; and only a single-iteration habitat model could be generated for a fourth species due to limited information data.

@@

		\subsection*{Distribution}

>>>>

\section*{Introduction}
	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863 (Curculionidae: Entiminae). 
	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
	Since the publication of the monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus}, based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} is given along with information on the geographic distribution of the herein described species.
	Where possible, we make note of host-plant records and briefly consider the historical biogeographic relationships of the new species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision.

\section*{Materials and methods}
	The keen reader will note a certain similarity between the methods used in this manuscript with those of Jansen and Franz 2015. 
	Rather than merely referencing the monograph as a source of inspiration, we feel it is better to provide a fully transparent and updated accounting of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most notably, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
	\paragraph{Natural history observations} 
		Members of the genus \textit{Minyomerus} may be found on a variety of host plants, as indicated following each description.
		While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, Mexico. 
		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

	\paragraph{Acquisition of museum specimens} 
		Georeferencing of localities was performed with Google Earth (Google Inc. 2009–2015) and reported in decimal degrees.
		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2017).
		The existing set of \textit{Minyomerus} specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al. (1993):

@@

	\paragraph{Morphological analysis}
		Our systematic and descriptive approach is complementary to Jansen and Franz 2015, which in turn follows Franz (2010a, 2010b, 2012).
		Terminology for exterior morphology is in general accordance with Torre-Bueno (Nichols 1989).
		Additional morphological terms specific to (entimine) weevils were used as follows:
			Ting (1936) and Morimoto and Kojima (2003) for mouthparts;
			Thompson (1992) for tibial apices and abdominal segments;
			and Oberprieler et al. (2014) and Howden (1995) for male and female terminalia.

		Measurements were taken with a Leica M205 C stereomicroscope and associated software, Leica Application Suite (LAS), version 4.1.0.
		Overall body length and width were measured in dorsal view as the maximum distance between the rostral and elytral apices, and the maximum width of both elytra, respectively.
		Rostral length was measured in dorsal view as the distance between the epistomal apex and the anterior margin of the eyes.
		Rostral width was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		Pronotal length was measured in dorsal view as the length along the midline between the anterior and posterior margins.
		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.

		Herein recognized species of \textit{Minyomerus}  were delimited through application of the phylogenetic species concept \textit{sensu} Wheeler and Platnick (2000).
		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but except those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} is arranged with emphasis being placed on the most readily observable diagnostic characters.
		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

@@

		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.

@@

		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al. 2004, 2006; Elith et al. 2011).

@@

		However, no models could be created for one species a single documented locality.

@@
